Strict Pure Functional Programming and Automatic Parallelization\\ (New-project-in-progess Paper)

### 2016-03-18 pubs/tfp16/paper.tex
TFP paper: more tweaks to testing section

We have implemented a simple copying garbage collector \cite{Cheney:1970}
with small "nurseries" in the multithreaded case \cite{Marlow:2008}. We have not
focused on the development of a moire sophisticated garbage collector, as the goal
of this project is to explore levels of strictness.

@@

There are several hundred small STG and mini-Haskell programs in the test suite.
It is partitioned into a number of directories which control what
testing is done for a specific program. Given our goal of exploring various
levels of strictness, most tests are run with all evaluation strategies (3
degrees of function strictness by two degrees of constructor strictness).
One interesting class of test programs are those which require non-strict
semantics. For these programs we test not only that the test leads to the expected
result with non-strict semantics, but also that the program returns a
"blackhole" in the case of strict semantics. Students who were Haskell/STG
beginners have contributed substantially to the test suite. We have also found
that the test suite has be of use as a learning tool for these students to
discover  what level of non-strictness was required for their programs,
a benefit that we did not initially envision. Over time we have developed
extensive STG and mini-haskell preludes of common programming patterns, to
aid in the writing of test programs.

Another important class of test programs are those which should fail with a
known error (e.g. a parsing error) for these programs the test suite checks
the output against an expected error regular expression. This class of test
programs has proved valuable in development and debugging of both the STG
and mini-haskell frontends.

@@

>>>>

We have implemented a simple copying garbage collector \cite{Cheney:1970}
with small "nurseries" in the multithreaded case \cite{Marlow:2008}. We have not
focused on the development of a more sophisticated garbage collector, as the goal
of this project is to explore levels of strictness.

@@

There are several hundred small STG and mini-Haskell programs in the test suite.
It is partitioned into a number of directories which control what
testing is done for a specific program. Given our goal of exploring various
levels of strictness, most tests are run with all evaluation strategies (3
degrees of function strictness by two degrees of constructor strictness).
One interesting class of test programs are those which require non-strict
semantics. For these programs we test not only that the test leads to the expected
result with non-strict semantics, but also that the program returns a
"blackhole" in the case of strict semantics. Students who were Haskell/STG
beginners have contributed substantially to the test suite. We have also found
that the test suite has be of use as a learning tool for these students to
discover  what level of non-strictness was required for their programs,
a benefit that we did not initially envision. Over time we have developed
extensive STG and mini-Haskell preludes of common programming patterns, to
aid in the writing of test programs.

Another important class of test programs are those which should fail with a
known error (e.g. a parsing error) for these programs the test suite checks
the output against an expected error regular expression. This class of test
programs has proved valuable in development and debugging of both the STG
and mini-Haskell front-ends.

@@

The various enumerations of strictness and garbage collection levels mean that
we run a quite large number of tests. However, this is fully automated via the
testing and continuous integration infrastructure.
